% -- Encoding UTF-8 without BOM
% -- XeLaTeX => PDF (BIBER)

\documentclass[]{cv-style}          % Add 'print' as an option into the square bracket to remove colours from this template for printing. 
                                    % Add 'espanol' as an option into the square bracket to change the date format of the Last Updated Text

\sethyphenation[variant=british]{english}{} % Add words between the {} to avoid them to be cut 

\begin{document}
\usepackage[papersize={8.5in,11in}]{geometry}

\header{Nathaniel}{~Felsen}
\lastupdated

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION  -- In the aside, each new line forces a line break
%----------------------------------------------------------------------------------------

\begin{aside}
%
\section{contact}
347~Lisbon~St
San~Francisco, CA~94112
+1~(408)~832-1745
nfelsen@gmail.com
~
Green card holder
%
\section{core engineering}
Architecting, Automation, System, Network, Security, Scaling, Deploying, Logging, Algorithmic, Unit~Testing, Troubleshooting
\section{scripting \& programming}
Python, Bash, Perl
\section{runtimes}
Bare metal, VM, Containers, Public\,Cloud, Private\,Cloud
\section{AI Infrastructure}
GPU, Parallel\,filesystems, Slurm, BCM, Infiniband, RoCE
\section{datastores}
MySQL, PostgreSQL, Redis, HDFS, HBase, ElasticSearch, RDS, Bloomd, Neo4j, Weka
\section{monitoring}
Prometheus, Grafana, Datadog, Splunk, ELK, Open telemetry
\section{configuration management}
Ansible, Puppet, Terraform, Helm, CloudFormation
\section{soft skills}
Leadership, People\,management, Project\,management, Incident\,response
%
\end{aside}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}


\begin{entrylist}
%------------------------------------------------
\entry
{Feb 2018 \newline
Dec 2024}
{Tesla}
{Palo Alto, California}
{\jobtitle{SRE, HPC and AI Infrastructure \hfill Nov '22 to Dec '24} \\
Led AI infrastructure development and operations, improving cluster deployments, monitoring, and security with a strong emphasis on automation.
\begin{itemize}
\item Deployed multiple large clusters (over 100K GPUs in multiple datacenters)
\begin{itemize}
    \item Utilized H100, A100, A40, MI250, and MI300x
    \item Implemented Infiniband and RoCEv2 for networking
    \item Used Weka for parallel filesystem
\end{itemize}
\item Developed and led a team of engineers to build Tesla’s HPC platform, adopting new technologies and spearheading Kubernetes integration within the organization.
\item Implemented fully automated bare-metal server provisioning by integrating Netbox, MAAS, Vault, Ansible, and Python scripts, streamlining processes and improving efficiency.
\item Centralized and automated BIOS configuration management.
\item Enhanced monitoring capabilities by introducing
\begin{itemize}
    \item A comprehensive monitoring of hardware and infrastructure services
    \item Prometheus and many custom Prometheus exporters
    \item Log collection using Splunk
    \item Custom tools to remediate issues automatically
\end{itemize}
\item Strengthened security posture by
\begin{itemize}
    \item Implementing an egress management layer
    \item Collaborating with InfoSec teams to populate audit reports
    \item Integrating a custom IAM layer
    \item Adding an EDR solution
\end{itemize}
\item Successfully established an intern program, contributing to team growth and development.
\item Diagnosed and resolved issues and incidents.
\item Participated in the 24x7 on-call rotation.
\end{itemize}}
\entry
{}
{}
{}
{\jobtitle{SRE, Vehicle Software - Data Platforms \hfill Feb '18 to Nov '22}  \\
Led the infrastructure development for a groundbreaking hybrid cloud data platform. Orchestrated the handling of trillions of events per day from diverse sources, including cars, factories, and energy products, leveraging open-source technologies and cloud services. Drove innovation in a data-centric world, delivering unparalleled scalability, performance, security, and durability.
\begin{itemize}
\item Architected the first iteration of the platform on-prem using Hadoop on bare metal servers to handle urgent needs.
\item Migrated services to run in Kubernetes using Helm.
\item Reimplemented the platform using a hybrid cloud-native approach, leveraging AWS on top of our private cloud.
\item Implemented CI/CD using Bazel and Jenkins.
\item Implemented monitoring using Prometheus, Cloudwatch, Grafana, and Splunk.
\item Made the platform multi-cloud with a presence worldwide, including in China and Europe.
\item Ensured GDPR compliance for the platform.
\item Troubleshot issues and incidents.
\item Participated in the 24x7 on-call rotation.
\end{itemize}\vspace{+10pt}}


%------------------------------------------------
\end{entrylist}
%------------------------------------------------
\newpage
%------------------------------------------------

\begin{entrylist}
%------------------------------------------------
\entry
{Jun 2014 \newline 
Feb 2018}
{Medium}
{San Francisco, California}
{\jobtitle{DevOps Engineer}\\
\begin{itemize}
\item Transformed Medium into a DevOps-centric organization
\begin{itemize}
\item Educated the engineering organization on goals and best practices.
\item Created an IAC Infrastructure using CloudFormation and Ansible.
\item Developed continuous integration and continuous deployment pipelines for services.
\item Created a highly scalable logging infrastructure using ELK and Kinesis.
\item Introduced new SaaS tools to better monitor metrics and trace requests.
\item Collected top-level metrics to track engineering efforts.
\end{itemize}
\item Took over management of the team called the Watch.
\begin{itemize}
\item On-boarded and coached new team members.
\item Scheduled on-call rotation.
\item Reported team activity and business key metrics to the broader organization.
\item Created documentation to assist with on-call work.
\item Took over Quality Engineering efforts.
\item Troubleshot issues and incidents.
\end{itemize}
\item Managed the various databases in our infrastructure.
\begin{itemize}
\item Improved overall performance and cost of DynamoDB.
\item Scaled Neo4j to handle the current QPS and dataset.
\item Migrated internal services from Redis to ElastiCache.
\item Introduced new databases, including RDS Aurora.
\item Created backup systems to secure our databases in other AWS accounts.
\end{itemize}
\item Brought AWS expertise to Medium.
\begin{itemize}
\item Migrated from AWS classic to VPC.
\item Provided regular presentations on new AWS technologies.
\item Moved services to Docker / ECS.
\item Architected new services to better leverage AWS services.
\item Created ETL pipelines to stream data from DynamoDB to Redshift using Lambda.
\item Added multiple CDNs to our architecture.
\item Implemented DDOS protection and rearchitected load balancing for better scalability.
\end{itemize}
\item Migrated Superfeedr to AWS.
\item Conducted onboarding presentations on our architecture for new hires.
\end{itemize}\vspace{+10pt}}
%------------------------------------------------
\entry
{Mar 2013 \newline Jun 2014}
{Jive Software}
{San Francisco, California}
{\jobtitle{DevOps Engineer and Service Architect} \\
\begin{itemize}
\item Created a complete solution for CI/CD for legacy and new services.
\item Participated in creating the company's internal framework to manage services.
\item Managed all multi-tenant customer-facing services.
\item Automated provisioning and orchestration of resources.
\item Puppetized a number of services previously managed by hand.
\item Added numerous DevOps tools to our infrastructure.
\item Deployed a solution to manage logs (Logstash, Kibana, Elasticsearch).
\item (Re)Architected several services to comply with industry best practices.
\item Improved infrastructure monitoring.
\item Administered Hadoop and HBase clusters.
\item Troubleshot issues and incidents.
\item Added documentation and processes to hand off service management to other teams.
\end{itemize}\vspace{+10pt}}
%------------------------------------------------
\end{entrylist}
%------------------------------------------------
\newpage
%------------------------------------------------

\begin{entrylist}
%------------------------------------------------
\entry
{Sept 2012\\Feb 2013}
{Square}
{San Francisco, California}
{\jobtitle{Service Reliability Operation Engineer} \\
\begin{itemize}
\item Joined Square as the first member of the SROE organization
\item Created \& documented all aspects of building SROE team (runbooks, checklists, change policies…)
\item Defined the team roadmap as well as work prioritization
\item Ran daily and weekly meetings on Change management (ITSM) and Infrastructure metrics review 
\item Made daily changes to our infrastructures in staging and production
\item Supported the engineering team with operations tasks (supplied hardware, created vips, db, dns changes etc…)
\item Monitored infrastructure
\item Troubleshot issues and incidents 
\item Took part of the 24x7 oncall rotation
\end{itemize}\vspace{+10pt}}

%------------------------------------------------
\entry
{Sept 2010\\Sept 2012}
{OnLive}
{Palo Alto, California}
{\jobtitle{Lead Service Reliability Engineer} \\
\begin{itemize}
\item Led a team of SRE of varying skill levels across multiple shifts (2 deeps), including weekend and grave
\item Ensured that tasks and projects get proper execution and resources
\item Monitored infrastructure
\item Added new monitoring scripts and tools to gain visibility on the platform and services
\item Developed new commands to operate the infrastructure 
\item Automated recurring tasks
\item Re-architected services to make them more reliable 
\item Trained new employees
\item Improved, Updated and Added documentations of our process in the wiki
\item Rolled out new code and new content to production 
\item Troubleshot issues and incidents
\item Post mortem analyses
\end{itemize}\vspace{+10pt}}
%------------------------------------------------
\entry
{Aug 2007\\Sept 2010}
{Orb Networks (Acquired by Qualcomm)}
{Oakland, California}
{\jobtitle{Server Operations / Linux Developer} \\
\begin{itemize}
\item Managed the operations: Responsible for System, Network and Security of the development, pre-production and production environment
\item Ported our desktop application Orb Caster to Linux (RPM/Deb and partners appliances)
\item Developed embedded software for orb’s home consumer products Orb Music and Orb TV
\item Improved the architecture of the web applications Mycast V1 and V2
\item Redesigned the database architecture schema to get high availability and geographic load balancing
\item Automated recurring tasks (build \& release of software, firmware, website, sales tax report)
\item Developed, integrated and deployed server side applications for streaming, crash reporting, registration
\end{itemize}}
\end{entrylist}

%------------------------------------------------
\newpage
%------------------------------------------------

\begin{entrylist}
%------------------------------------------------
\entry
{Mar 2006\\Aug 2007}
{Qualys}
{Redwood Shores, California}
{\jobtitle{Linux System Administrator} \\
\begin{itemize}
\item Managed Staging, Quality Assurance and Development servers that are involved in running the QualysGuard service. 
\item Developed web based tools and applications for Setup, Administration, Maintenance and Troubleshooting of the production environment 
\item Built and deployed new server hardware for the QualysGuard service. 
\item Performed ongoing system maintenance, administration, and troubleshooting. 
\item Deployed new systems and security patches. 
\item Analyzed performance and identify system bottlenecks
\item Made a proof of concept on the log management 
\item R\&D on the integration of QualysGuard in open source and commercial solutions
\end{itemize}}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	publication
%----------------------------------------------------------------------------------------

\section{publication}

\begin{entrylist}
%------------------------------------------------
\entry
{Jul 2017}
{Effective DevOps with AWS}
{Packt Publishing}
{}

%------------------------------------------------
\entry
{Sept 2018}
{Effective DevOps with AWS - 2nd edition}
{Packt Publishing}
{Scale gracefully and maintain outstanding performance with your AWS-based infrastructure using DevOps principles -- still available on amazon.com}
%------------------------------------------------
\end{entrylist}


%----------------------------------------------------------------------------------------
%	Additional Experience
%----------------------------------------------------------------------------------------

\section{additional experience}
\begin{entrylist}
%------------------------------------------------
\entry
{Aug 15\\Aug 18}
{Holberton School of Software Engineering}
{San Francisco, California}
{\emph{Mentor} \\
\vspace{-10pt}\begin{itemize}
\item Interacting regularly with students to talk about real-life software engineering issues.
\item Mentoring students through their formations
\end{itemize}}

\entry
{Feb 08\\Oct 08}
{Acadopia}
{San Francisco, California}
{\emph{Technical co-founder } \\
\vspace{-10pt}\begin{itemize}
\item Chose the technologies and tools to use for the initial product
\item Architected the application
\item Developed the application with 2 other engineers
\end{itemize}}
\entry
{Dec 07\\Feb 08}
{NewsBox Facebook application}
{San Francisco, California}
{\emph{Web Developer} \\
\vspace{-10pt}\begin{itemize}
\item Architected the server infrastructure
\item Developed the Back-End, Front-End and User Interface
\end{itemize}}
\entry
{Mar 05\\Dec 05}
{Hawkeye}
{Paris, France}
{\emph{Developer} \\
Took part in developing the open source project, hawkeye}
\entry
{Jan 05\\Dec 05}
{Cristal}
{Paris, France}
{\emph{Security consultant (contractor)} \\
\vspace{-10pt}\begin{itemize}
\item Involved with 2-3 application/network penetration tests a month.
\item Created Reports for the client during the vulnerability discovery, remediation and mitigation processes.
\end{itemize}}
\entry
{Jan 05\\Dec 05}
{Epita}
{Paris, France}
{\emph{Teacher’s Assistant} \\
Taught engineering students C, Unix programming and algorithmic}


\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{education}

\begin{entrylist}
%------------------------------------------------
\entry
{2024}
{Engineering Leadership Certificate}
{Cornell University}
{}
%------------------------------------------------
\entry
{2001--2006}
{Master's {\normalfont in Computer Science (MSCS)}}
{EPITA, Paris, France}
{Graduated with honors}
%------------------------------------------------
\end{entrylist}
\end{document}